---
title: "Assignment5"
author: "Jae Eun Hong"
date: "10/5/2021"
output: html_document
---

## Libraries 
```{r message=FALSE, warning=FALSE}

library(tidyverse)
library(readxl)
library(dplyr)
library(ggplot2)
library(magrittr)
library(RColorBrewer)
library(babynames)
library(barnnamn)
```


## 1. Reversing classification 
```{r message=FALSE, warning=FALSE}
# Simplified csv file of kelly data
temp_data <- read.csv('C:/Users/wk789/Documents/school/UU/data visualisation/assignment5/japankoppenextra.csv')

climateclass <- function(temperatures){
  
  
  
  if(min(temperatures) < 10 & max(temperatures) < 10){
    return ("E")
  } else if(min (temperatures) < 0 & max(temperatures) > 10) {
    return ("D")
  } else if(min(temperatures) > 0 & min(temperatures) < 18 & max(temperatures) > 10){
    return ("C")
  } else{
    return ("A")
  } 
}

city_climate <- tibble(city = character(), 
                       climate = character())

for(c in temp_data %>% pull(city) %>% unique()){

  city_data <- temp_data %>% filter(city == c) %>%  pull( daily_mean)

  clim <- climateclass(city_data)
  city_climate <- city_climate %>% add_row(city = c, climate = clim)

}

city_climate
```

## 2. Further climate subdivisions 
```{r message=FALSE, warning=FALSE}

climateclass <- function(temperatures, precipitations){
  
  # storing summer / winter precipitation into a variable
  summer_prec <- precipitations %>% filter(month %in% c(6, 7, 8)) %>% pull(precipitation)
  
  winter_prec <- precipitations %>% filter(month %in% c(12, 1, 2)) %>% pull(precipitation)
  
  
  if(min(temperatures) < 10 & max(temperatures) < 10){
    return ("E")
  }
  
  else if(min (temperatures) < 0 & max(temperatures) > 10) {
    if(max(summer_prec) > min(winter_prec) * 10) {
      return("Dw")
    }
    else if( max(winter_prec) > min(summer_prec) * 3 & min(summer_prec) < 40) {
      return("Ds")
    }
    else{
      return("Df")
    }
  } 
  
  else if(min(temperatures) > 0 & min(temperatures) < 18 & max(temperatures) > 10){
    if(max(summer_prec) > min(winter_prec) * 10) {
      return("Cw")
    }
    else if( max(winter_prec) > min(summer_prec) * 3 & min(summer_prec) < 40) {
      return("Cs")
    }
    else{
      return("Cf")
    }
  } 
  
  else{
    return ("A")
  } 
}

city_climate <- tibble(city = character(), 
                       climate = character())

for(c in temp_data %>% pull(city) %>% unique()){

  city_data <- temp_data %>% filter(city == c) %>%  pull( daily_mean)
  precipitation_data <- temp_data %>% filter(city == c) %>% select(c(month, precipitation))

  clim <- climateclass(city_data, precipitation_data)
  city_climate <- city_climate %>% add_row(city = c, climate = clim)

}

city_climate

```


## 3. RE with Barnnamn data

```{r message=FALSE, warning=FALSE}
vowel_pattern = "^[AEIOUYÅÄÖ]"


vstart_names <- barnnamn$name %>% str_subset(vowel_pattern)

vstart_data <- barnnamn %>% 
  filter(name %in% vstart_names) %>% 
  group_by(year, sex) %>% 
  summarise(total = sum(prop)) %>% 
  mutate(start="vowel")

vstart_data

cstart_names <- barnnamn$name %>% str_subset(vowel_pattern, negate=TRUE)

cstart_data <- barnnamn %>% 
  filter(name %in% cstart_names) %>% 
  group_by(year, sex) %>% 
  summarise(total = sum(prop)) %>% 
  mutate(start="consonant")

final_data <- rbind(vstart_data, cstart_data)

ggplot(final_data, aes(x = year, y = total, colour = sex)) + facet_wrap(~start) + geom_line(lwd=1)+ scale_color_brewer(palette = "Accent") +
  ggtitle("Swedish names starting with consonants/vowels")+
  theme(legend.position = "right",
        plot.title = element_text(
          size = rel(1.2), lineheight = .9,
          family = "Calibri", face = "bold", colour="darkseagreen4"
        ))

```


Names starting with a consonant is more common than the ones with a vowel on both sex. The distribution of male names beginning with consonants are inversely proportional to names beginning with vowels.



```{r message=FALSE, warning=FALSE}


vstart_data_for_vowel_plot <- barnnamn %>% 
  filter(name %in% vstart_names) %>% 
  mutate(start = str_extract(name, '^.{1}')) %>% 
  group_by(year, sex, start)%>% 
  summarise(total = sum(prop))
  
# vstart_data_for_vowel_plot

ggplot(vstart_data_for_vowel_plot
, aes(x = year, y = total, colour = sex)) + facet_wrap(~start) + geom_line(lwd=1)+ scale_color_brewer(palette = "Accent") +
  ggtitle("Swedish names starting with vowels")+
  theme(legend.position = "right",
        plot.title = element_text(
          size = rel(1.2), lineheight = .9,
          family = "Calibri", face = "bold", colour="darkseagreen4"
        ))


```


The vowel 'A' and 'E' are favoured by both gender. However, for male, the vowel 'A' is most popular for male, and for female, the vowel 'E' is most popular. The special vowels that exist in Swedish (Å, Ö, Ä and Y) are rarely used in both gender. The fact that 'Ä' is only used in female name and 'Ö' in male name through out the time is an interesting point. It is also intriguing that the vowel 'Å' is seldom used for female name till early 2000s and lost the popularity among female name. 



## 4. RE with babynames data 

```{r message=FALSE, warning=FALSE}

girls <- babynames %>% filter(sex=='F') %>% group_by(name) %>% summarise(total=sum(n)) %>% arrange(desc(total)) %>% head(5)
girls
```
```{r message=FALSE, warning=FALSE}
# mary variant pattern
# Maaria, Maaarja, Mari, Maria, Mariam, Marie
mary = 'Ma{1,2}r[ij][ae]?.*' 

# elizabeth variant pattern 
# Eliza, Elisa, Elissa, Elisabet..
eliza = 'Eli[sz]{1,2}[ae].*'

# patricia variant pattern 
# Patti, Pattie... 
patricia = 'Pat{1,2}.*'

# jeniffer variant pattern 
jennifer = 'Jen+.*'

# linda variant pattern 
#Lindy, lyn, lynda,...

linda = 'L[iy]n.*'

mary_variant <- babynames%>% filter(sex=='F') %>% .$name  %>% str_subset(mary)
eliza_variant <- babynames%>% filter(sex=='F') %>% .$name  %>% str_subset(eliza)
patricia_variant <- babynames%>% filter(sex=='F') %>% .$name  %>% str_subset(patricia)
jennifer_variant <- babynames%>% filter(sex=='F') %>% .$name  %>% str_subset(jennifer)
linda_variant <- babynames%>% filter(sex=='F') %>% .$name  %>% str_subset(linda)



mary_data <- babynames %>% filter(sex=='F') %>% 
  filter(name %in% mary_variant) %>% 
  group_by(year) %>% 
  summarise(total = sum(n)) %>% 
  mutate(original="Mary")

eliza_data <- babynames %>% filter(sex=='F') %>% 
  filter(name %in% eliza_variant) %>% 
  group_by(year) %>% 
  summarise(total = sum(n)) %>% 
  mutate(original="Elizabeth")


patricia_data <- babynames %>% filter(sex=='F') %>% 
  filter(name %in% patricia_variant) %>% 
  group_by(year) %>% 
  summarise(total = sum(n)) %>% 
  mutate(original="Patricia")

jennifer_data <- babynames %>% filter(sex=='F') %>% 
  filter(name %in% jennifer_variant) %>% 
  group_by(year) %>% 
  summarise(total = sum(n)) %>% 
  mutate(original="Jennifer")

linda_data <- babynames %>% filter(sex=='F') %>% 
  filter(name %in% linda_variant) %>% 
  group_by(year) %>% 
  summarise(total = sum(n)) %>% 
  mutate(original="Linda")

final_data <- rbind(mary_data, eliza_data, patricia_data, jennifer_data, linda_data)

final_data <- final_data %>% group_by(original) %>% summarise(total=sum(total)) %>% arrange(desc(total)) %>% head(5)

final_data
```

Most of the order has been changed after the recalculation of the totals across all variants except for the name Mary. 

